\documentclass[a4paper,11pt]{article}
% \pdfoutput=1
\usepackage{jcappub}
% \usepackage[T1]{fontenc} % if needed
\usepackage{amsmath}
\usepackage{amssymb}

\DeclareRobustCommand{\ion}[2]{%
\relax\ifmmode
\ifx\testbx\f@series
{\mathbf{#1\,\mathsc{#2}}}\else
{\mathrm{#1\,\mathsc{#2}}}\fi
\else\textup{#1\,{\mdseries\textsc{#2}}}%
\fi}

\usepackage{enumitem}
\setlist[enumerate]{itemsep=1mm}

\newcommand{\lya}{Lyman-$\alpha$~}
\newcommand{\Lya}{Lyman-$\alpha$~}
% martin comment function
\newcommand{\maf}[1]{{\textcolor{red}{[{\bf MAF}: #1]}}}
% simeon comment function
\newcommand{\spb}[1]{{\textcolor{magenta}{[{\bf SPB}: #1]}}}
% ming-feng comment function
\newcommand{\mfho}[1]{{\textcolor{green}{[{\bf MFH}: #1]}}}

\newcommand{\apjs}{ApJ Supplement}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{ApJL}

\newcommand{\aap}{AAP}
\newcommand{\mnras}{MNRAS}
\newcommand{\prd}{PRD}
\newcommand{\prl}{PRL}
\newcommand{\jcap}{JCAP}

%\title{\boldmath Inference via a \lya Forest Emulator}
\title{\boldmath Cosmological Constraints from the eBOSS \lya Forest using the PRIYA Simulations}

\author{M.A. Fernandez,}\emailAdd{mfern027@ucr.edu}
\author{Simeon Bird}\emailAdd{sbird@ucr.edu}
\author{and Ming-Feng Ho,}\emailAdd{mho026@ucr.edu}
\affiliation{Department of Physics and Astronomy, University of California Riverside, 900 University Ave, Riverside, CA 92521}

\abstract{
We present new cosmological parameter constraints from the eBOSS \lya forest survey. We use a new theoretical model and likelihood based on the PRIYA simulation suite. PRIYA is the first suite to resolve the \lya forest in a ($120$~Mpc/h~)$^3$ volume, using a multi-fidelity emulation technique. We use PRIYA to predict \lya forest observables with $\lesssim 1\%$ interpolation error over an $11$ dimensional ($9$ simulated, $2$ in post-processing) parameter space. We identify an internal tension within the flux power spectrum data. 
Once the discrepant data is removed, we find the primeval scalar spectral index measured at a pivot scale of $k_0 = 0.78$ Mpc$^{-1}$ to be $n_P = 1.009^{+0.027}_{-0.018}$ at 68\% confidence. This measurement from the \lya forest flux power spectrum alone is in \textbf{reasonable} agreement with Planck, and in tension with earlier eBOSS analyses. The amplitude of matter fluctuations is $\sigma_8 = 0.733^{+0.026}_{-0.029}$ at 68\% confidence, in agreement with Dark Energy Survey weak lensing measurements and other small-scale structure probes and in tension with CMB measurements from Planck and ACT. The effective optical depth to \lya photons from our pipeline is in good agreement with earlier high resolution measurements. \textbf{We find a linear power at $z=3$ and $k = 0.009$ s/km of $\Delta_L^2 = 0.302^{+0.024}_{-0.027}$ with a slope $n_\mathrm{eff} = -2.264^{+0.026}_{-0.018}$. Our flux power spectrum only chains prefer a low level of heating during helium reionization. When we add IGM temperature data we find $n_P = 0.983\pm 0.020$ and $\sigma_8 = 0.703^{+0.023}_{-0.027}$.
Our chains prefer an early and long helium reionization event, as suggested by measurements from the helium \lya forest.}
In the near future we will use our pipeline to infer cosmological parameters from the DESI \lya data.
}


\begin{document}
\maketitle
\flushbottom
% - Different seed cosmic variance chain added to section 3.3
% - Plot like loo_vs_emu_error_wlegend.pdf but for z=2.2 - 2.6 and use it as main result, rather than the shrunk corner plots.
% - Drop LOO from the 'full posteriors' figure. Add 'with mean temperature'? Or just leave it alone?
%
% Main conclusion:
% There is a discrepancy between the z=2.2-2.4 and z >= 2.6 bins. This drives tensions across the whole parameter space. Clear from the best fit.

\input{sections-v2/introduction}
\input{sections-v2/emulator}
\input{sections-v2/inference}
\input{sections-v2/results}
\input{sections-v2/conclusions}

\acknowledgments
MAF is supported by a National Science Foundation Graduate Research Fellowship under grant No. DGE-1326120.
SB was supported by NSF grant AST-1817256 and by NASA-80NSSC21K1840. 
MQ was supported by NSF grant AST-2107821. 
MFH is supported by a NASA FINESST grant No. ASTRO20-0022.
Computing resources were provided by Frontera LRAC AST21005.
The authors acknowledge the Frontera computing project at the Texas Advanced Computing Center (TACC) for providing HPC and storage resources that have contributed to the research results reported within this paper.
Frontera is made possible by National Science Foundation award OAC-1818253.
URL: \url{http://www.tacc.utexas.edu}. Analysis computations were performed using the resources of the UCR HPCC, which were funded by grants from NSF (MRI-2215705, MRI-1429826) and NIH (1S10OD016290-01A1).

\appendix
\input{sections-v2/appendices}

% --------------------------------------------------------------------------------------------------

\bibliographystyle{JHEP.bst}
\bibliography{refs}

\end{document}
